Developing Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set

### 2023-08-24 paper.tex
Update Appendix and Title page

%%% Additional Packages %%%
\usepackage{cite}
\usepackage{framed}
\usepackage{graphicx}
%\usepackage[german]{fancyref}
\usepackage[german,hidelinks]{hyperref} %hidelinks
\usepackage{multirow}
\usepackage[round]{natbib}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{pst-all} % Not working with Sweave!!!
\usepackage{tikz}
\usetikzlibrary{positioning, intersections}
\usepackage{subcaption}

@@

%%% Document Specifications %%%
\title{Template Master's Thesis}
\author{John Doe}

@@

\begin{document}
%\begin{titlepage}
\begin{center}
\vspace{1em}
\large{Master Thesis}\\
\LARGE Developing Address Clustering Heuristics for Account-Based Blockchain Networks:\\ An Analysis based on a Specific Address Set \\
\Large \vspace{1em}
Dario Thürkauf
\end{center}

@@

\vfill
\textbf{Keywords:} Blockchain, Accounts, Clustering Heuristics, Entity Identification, Graph Representation Learning.\\
%\noindent\textbf{JEL:} X00, X00, X00
%\end{titlepage}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{../figures/land-opensea.png}
	\caption{Example of LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
	\label{fig:LAND_example}
\end{figure}

@@

\begin{table}[h!]
\scriptsize
  \centering
  \begin{tabular}{lrrr}
    \hline
	\textbf{ENS domain name} & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
	\hline
	anisofim.eth & 2.5 & 6.2 & 2.7 \\
	arisalzberg.eth & 577.3 & 33.3 & 58.8 \\
	atearnz.eth & 2.8 & 2.5 & 3.3 \\
	awedjob.eth & 106.8 & 71.1 & 20.1 \\
	captvicky.eth & - & - & - \\
	disruptor.eth & 11.1 & 3.0 & 1.4 \\
	dragonkiller.eth & 30.7 & 1.0 & 1.0 \\
	eibriel.eth & 44.3 & 91.2 & 545.4 \\
	epdrabbit.eth & 16.3 & 10.4 & 4.1 \\
	erikarand.eth & 1.0 & 1.0 & 1.0 \\
	hyperspek.eth & 129.1 & 10.0 & 605.4 \\
	jamesmillerblog.eth & - & - & - \\
	jasonhsu.eth & 1.0 & 1.0 & 1.8 \\
	joeyz.eth & 1.9 & 1.0 & 1.0 \\
	keastie.eth & 10.4 & 1.0 & 18.2 \\
	linkg.eth & 4.0 & 1.0 & 10.3 \\
	lulox.eth & 4.2 & 1.5 & 27.2 \\
	maruudn.eth & 5.7 & 5.6 & 108.5 \\
	maryana.eth & 52.3 & 373.8 & 9.0 \\
	meanboss.eth & 9.0 & 9.0 & 51.8 \\
	metatiger.dcl.eth & 474.2 & 86.7 & 2.4 \\
	mgdivingnz.eth & 1.7 & 5.0 & 1.0 \\
	mrcryp.eth & 2.7 & 1.0 & 2.3 \\
	nicebhaiya.eth & 1.3 & 3.4 & 2.4 \\
	niceguy.eth & 1.0 & 1.0 & 2.2 \\
	ornellaweb3.eth & 3.7 & 2.0 & 284.0 \\
	pinkboots.eth & 16.9 & 14.4 & 2.2 \\
	remx.eth & 3.6 & 2.6 & 1.7 \\
	rileybeans.eth & 1.5 & 2.0 & 1.6 \\
	robertjames.eth & 2.7 & 1.0 & 1.1 \\
	rsantos.eth & 2.0 & 13.6 & 101.2 \\
	sannin.eth & 64.8 & 1.1 & 1.6 \\
	smileface.eth & 3.0 & 19.3 & 1.7 \\
	theartcollection.eth & 11.0 & 5.6 & 3.4 \\
	turkii13.eth & 52.1 & 68.9 & 47.3 \\
	tweetious.eth & 10.3 & 4.0 & 227.0 \\
    \hline
    Mean & 46.038 & 28.073 & 62.084 \\
    Median & 4.2 & 3.4 & 3.3 \\
    Standard deviation & 120.504 & 68.814 &  139.932\\
    Within 5 nearest neighbors & 17 (0.5) & 19 (0.56) & 20 (0.59) \\
    Within 10 nearest neighbors & 19 (0.56) & 24 (0.71) & 21 (0.62)\\
    \hline
  \end{tabular}
  \caption{Average Rank of ENS Domain Names for Different Embedding Methods}
  \label{tbl:ENS_Domain_Ranks}
\end{table}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
	\caption{Resulting LAND clusters, with largest cluster marked in green}
	\label{fig:LAND_clusters}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.65\textwidth]{../figures/network_visualization_0xe2e.png}
	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
	\label{fig:cluster}
\end{figure}

@@

@@

%% Table
\begin{table}[h!]
  \centering
  \tiny
  \begin{tabular}{ll p{4cm} l}
    \hline
    \textbf{Collection} & \textbf{Fields} & \textbf{Description} & \textbf{Example} \\ \hline
    Transactions & \texttt{\_id} & Unique identifier & 64b3c65ed2daf924bfdce72b
 \\
    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
     & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
     & \texttt{gasUsed} & Amount of gas used by the transaction &  144176  \\
     & \texttt{gasPrice} & The price of gas the originator is willing to pay &  12449848873 \\
     & \texttt{nonce} &   &   \\
     & \texttt{from} & Address initiating the transaction &   \\
     & \texttt{to} & The destination address (either native asset transfer or function call) &  \\
     & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
     & \texttt{input} & Calldata & 0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff \\
     & \texttt{functionName} & added by Etherscan & approve(address spender, uint256 rawAmount) \\
     & \texttt{chainName} & Chain indicator & Ethereum or Polygon \\
    \hline
    Transfers & \texttt{\_id} & see above & see above\\
    (36.4M rows) & \texttt{hash} & see above & see above \\
     & \texttt{timeStamp} & see above & see above\\
     & \texttt{gasUsed} & see above &  see above\\
     & \texttt{gasPrice} & see above & see above \\
     & \texttt{nonce} &  see above & see above \\
     & \texttt{from} &  Sender address & see above \\
     & \texttt{to} &  Recipient address & see above \\
     & \texttt{value} & Amount of tokens transferred in Wei, only for fungible or semi-fungible tokens & 10000000000000000 or NaN (ERC-721) \\
     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  or NaN (ERC20) \\
     & \texttt{contractAddress} & The token contract address &  0xc02aaa39b223fe8d0a0e5c4f27ead9083c756cc2 \\
     & \texttt{tokenName} & The specified token name &  Wrapped Ether\\
     & \texttt{tokenType} & Token standard indicator &  20 or 721 or 1155\\
     & \texttt{chainName} & see above &  see above \\
     & \texttt{isSet} & Indicator if from or to address are from address set &  from or to \\
     & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
    \hline
  \end{tabular}
  \caption{Database/data set Description}
\end{table}

%Distinction: Transaction is a message sent from an externally owned account

>>>>

%%% Additional Packages %%%
\usepackage{cite}
\usepackage{framed}
\usepackage{graphicx}
%\usepackage[german]{fancyref}
\usepackage[german,hidelinks]{hyperref} %hidelinks
\usepackage{multirow}
\usepackage[round]{natbib}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{pst-all} % Not working with Sweave!!!
\usepackage{tikz}
\usetikzlibrary{positioning, intersections}
\usepackage{subcaption}
\usepackage{seqsplit}

@@

%%% Document Specifications %%%
\title{Developing Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set}
\author{Dario Thürkauf}

@@

\begin{document}
\begin{titlepage}
\begin{center}
\vspace{1em}
\large{Master Thesis}\\
\LARGE Developing Address Clustering Heuristics for Account-Based Blockchain Networks:\\ An Analysis based on a Specific Address Set \\
\Large \vspace{1em}
Dario Thürkauf
\end{center}

@@

\vfill
\textbf{Keywords:} Blockchain, Accounts, Clustering Heuristics, Entity Identification, Graph Representation Learning.\\
%\noindent\textbf{JEL:} X00, X00, X00
\end{titlepage}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{../figures/land-opensea.png}
	\caption{LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
	\label{fig:LAND_example}
\end{figure}

@@

\begin{table}[h!]
\scriptsize
  \centering
  \begin{tabular}{lrrr}
    \hline
	\textbf{ENS domain name} & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
	\hline
	anisofim.eth & 2.5 & 6.2 & 2.7 \\
	arisalzberg.eth & 577.3 & 33.3 & 58.8 \\
	atearnz.eth & 2.8 & 2.5 & 3.3 \\
	awedjob.eth & 106.8 & 71.1 & 20.1 \\
	captvicky.eth & - & - & - \\
	disruptor.eth & 11.1 & 3.0 & 1.4 \\
	dragonkiller.eth & 30.7 & 1.0 & 1.0 \\
	eibriel.eth & 44.3 & 91.2 & 545.4 \\
	epdrabbit.eth & 16.3 & 10.4 & 4.1 \\
	erikarand.eth & 1.0 & 1.0 & 1.0 \\
	hyperspek.eth & 129.1 & 10.0 & 605.4 \\
	jamesmillerblog.eth & - & - & - \\
	jasonhsu.eth & 1.0 & 1.0 & 1.8 \\
	joeyz.eth & 1.9 & 1.0 & 1.0 \\
	keastie.eth & 10.4 & 1.0 & 18.2 \\
	linkg.eth & 4.0 & 1.0 & 10.3 \\
	lulox.eth & 4.2 & 1.5 & 27.2 \\
	maruudn.eth & 5.7 & 5.6 & 108.5 \\
	maryana.eth & 52.3 & 373.8 & 9.0 \\
	meanboss.eth & 9.0 & 9.0 & 51.8 \\
	metatiger.dcl.eth & 474.2 & 86.7 & 2.4 \\
	mgdivingnz.eth & 1.7 & 5.0 & 1.0 \\
	mrcryp.eth & 2.7 & 1.0 & 2.3 \\
	nicebhaiya.eth & 1.3 & 3.4 & 2.4 \\
	niceguy.eth & 1.0 & 1.0 & 2.2 \\
	ornellaweb3.eth & 3.7 & 2.0 & 284.0 \\
	pinkboots.eth & 16.9 & 14.4 & 2.2 \\
	remx.eth & 3.6 & 2.6 & 1.7 \\
	rileybeans.eth & 1.5 & 2.0 & 1.6 \\
	robertjames.eth & 2.7 & 1.0 & 1.1 \\
	rsantos.eth & 2.0 & 13.6 & 101.2 \\
	sannin.eth & 64.8 & 1.1 & 1.6 \\
	smileface.eth & 3.0 & 19.3 & 1.7 \\
	theartcollection.eth & 11.0 & 5.6 & 3.4 \\
	turkii13.eth & 52.1 & 68.9 & 47.3 \\
	tweetious.eth & 10.3 & 4.0 & 227.0 \\
    \hline
    Mean & 46.038 & 28.073 & 62.084 \\
    Median & 4.2 & 3.4 & 3.3 \\
    Standard deviation & 120.504 & 68.814 &  139.932\\
    Within 5 nearest neighbors & 17 (0.5) & 19 (0.56) & 20 (0.59) \\
    Within 10 nearest neighbors & 19 (0.56) & 24 (0.71) & 21 (0.62)\\
    \hline
  \end{tabular}
  \caption{Average Rank of Target Address}
  \label{tbl:ENS_Domain_Ranks}
\end{table}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
	\caption{LAND clusters, largest cluster marked in green}
	\label{fig:LAND_clusters}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/network_visualization_0xe2e.png}
	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
	\label{fig:cluster}
\end{figure}

@@

%\subsection{List of Figures}

%\subsection{List of Tables}

@@

%% Table
\begin{table}[h!]
  \centering
  \tiny
  \begin{tabular}{ll p{4cm} p{5.5cm}}
    \hline
    \textbf{Collection} & \textbf{Fields} & \textbf{Description} & \textbf{Example} \\ \hline
    Transactions & \texttt{\_id} & Unique identifier & 64b3c65ed2daf924bfdce72b
 \\
    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf... \\
     & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
     & \texttt{gasUsed} & Amount of gas used by the transaction &  144176  \\
     & \texttt{gasPrice} & The price of gas the originator is willing to pay &  12449848873 \\
     & \texttt{nonce} &   &   \\
     & \texttt{from} & Address initiating the transaction &   \\
     & \texttt{to} & The destination address (either native asset transfer or function call) &  \\
     & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
     & \texttt{input} & Calldata & \seqsplit{0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff} \\
     & \texttt{functionName} & added by Etherscan & approve(address spender, uint256 rawAmount) \\
     & \texttt{chainName} & Chain indicator & Ethereum or Polygon \\
    \hline
    Transfers & \texttt{\_id} & see above & see above\\
    (36.4M rows) & \texttt{hash} & see above & see above \\
     & \texttt{timeStamp} & see above & see above\\
     & \texttt{gasUsed} & see above &  see above\\
     & \texttt{gasPrice} & see above & see above \\
     & \texttt{nonce} &  see above & see above \\
     & \texttt{from} &  Sender address & see above \\
     & \texttt{to} &  Recipient address & see above \\
     & \texttt{value} & Amount of tokens transferred in Wei, only for fungible or semi-fungible tokens & 10000000000000000 or NaN (ERC-721) \\
     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  or NaN (ERC20) \\
     & \texttt{contractAddress} & The token contract address &  0xc02aaa39b223fe8d0a0e5c4f27ead9083c756cc2 \\
     & \texttt{tokenName} & The specified token name &  Wrapped Ether\\
     & \texttt{tokenType} & Token standard indicator &  20 or 721 or 1155\\
     & \texttt{chainName} & see above &  see above \\
     & \texttt{isSet} & Indicator if `from` or `to` address are from address set &  from or to \\
     & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
    \hline
  \end{tabular}
  %\caption{Database/data set Description}
\end{table}
%Distinction: Transaction is a message sent from an externally owned account

\subsection{Github Repos}
